Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-24 papers/actus2021/article.tex
tidying up formulas

\newcommand{\STF}{\ident{STF}}
\noindent 
\begin{equation*}
\ident{path}=\STF_{1}(ct,ev_{1})\circ \STF_{2}(ct,ev_{2}).\circ\ldots\circ \STF_{i}(ct,ev_{n})
\end{equation*}

\noindent 
\begin{equation*}
\ident{state}_{i}=\ident{path}(\ident{INIT}(ct)),
\end{equation*}
\noindent
where \emph{ct} stands for contract terms, \emph{INIT} returns initial state, \emph{sched}
returns scheduled events, \emph{STF} takes \emph{contractterms}, \emph{event}, and \emph{state}
and returns the next state, and \emph{POF} returns the payoff in a state.

>>>>

\newcommand{\STF}{\ident{STF}}
\noindent 
\begin{equation*}
\ident{path}_{i}=\STF(ct,ev_{1})\circ \STF(ct,ev_{2})\circ\ldots\circ \STF(ct,ev_{i})
\end{equation*}

\noindent 
\begin{equation*}
\ident{state}_{i}=\ident{path}_{i}(\ident{INIT}(ct)),
\end{equation*}
\noindent
where \emph{ct} stands for contract terms, \emph{INIT} returns initial state, \emph{sched}
returns scheduled events, \emph{STF} takes \emph{contract terms}, \emph{event}, and \emph{state}
and returns the next state, and \emph{POF} returns the \emph{payoff} from a state.
